### 2007-01-14 Documentation/part1.tex
JK - Minor corrections in chapters 5 and 6

In many cases, one can find the exact position of the 
$\mathrm{sgn}(\ldm)$-degeneracy with \GLB{ChiAll}, where one starts 
the local minimizer at the suspected position 
and let it run into the minimum.  The following code excerpt  corresponds to finding the degenerate solution for the example on
  page~\pageref{ex:corrth13dcp}, and it is from {\tt example3.c}: 
\begin{quote}
{\tt
{\footnotesize
  /* Set starting vales to suspected position at opposite sign of ldm */ \\
  \mbox{glbDefineParams(starting\_values,theta12,theta13,theta23,deltacp,sdm,-ldm);} \\
  glbSetDensityParams(starting\_values,1.0,GLB\_ALL); \\
  \\
  /* Set input errors for external input, where some information on ldm \\
   \hspace*{0.5cm} is imposed in order to avoid falling into the right-sign solution */ \\
  glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,ldm/3); \\ 
  glbSetDensityParams(input\_errors,0.05,GLB\_ALL); \\
  \\
  glbSetCentralValues(starting\_values); \\
  glbSetInputErrors(input\_errors); \\
  \\
  /* Localize degenerate solution by minimization over all parameters */ \\
  double CL=glbChiAll(starting\_values,deg\_pos,GLB\_ALL); \\
   \\
  \mbox{/* Now: CL is the chi2 of the deg.~solution and deg\_pos the position */} 
}}
\end{quote}

Using {\tt ent\_pos} to obtain a section of the degeneracy in the
$\stheta$-$\deltacp$-plane (\cf, {\tt example3.c}), one can plot it as a contour plot in addition to the original solution (2 d.o.f., gray curves):
\begin{center}
\colorbox{white}{\includegraphics[width=7.5cm]{correntex}}
\end{center}

@@

\label{mass_ordering}
\index{norm}{Mass hierarchy}
\paragraph{Note:} Inverting the mass hierarchy is not
precisely the same than to change from $\Delta m^2_{31}
\rightarrow -\Delta m^2_{31}$.
In this case the absolute value of $\Delta m^2_{32}$ changes also, which
introduces a new frequency to the problem. Therefore, if we assume
normal hierarchy  whenever $\Delta m^2_{31}>0$, the corresponding
point in parameters space for inverted hierarchy is given by $\Delta 
m^2_{31}\rightarrow - \Delta m^2_{31} + \Delta m^2_{21}$, because
with this defintion the absolute value of  $\Delta m^2_{32}$ is unchanged
and no new frequency is introduced.\\

@@

In addition to switching off the systematics, it can be useful to reduce the input errors during some steps of the localization process in order to make the minimizer not to run away too much from the targeted solution.

@@

\item[Manual scan of a subspace.] In some cases, the minimizer easily ends up in the wrong/unwanted solution, which is in most cases the already known best-fit solution. For example, for the octant degeneracy location, it is difficult to prevent the minimizer from running into the best-fit octant. In this case, one can scan one parameter (such as $\theta_{23}$) on a grid by choosing only valid values, and use {\tt glbChiNP} to marginalize over the other ones (while keeping \eg\ $\theta_{23}$ fixed). Therefore, the 6-parameter minimization is split into a 1-parameter manual minimization and a 5-parameter simultaneous minimization. Advantage: Runs with all \GLOBES\ versions. Disadvantage: Very slow. 

@@

 Altogether, there is a maximum of eight intersection points in the $\sin^2 2 \theta_{13}$-$\delta_{\mathrm{CP}}$-plane, one of which is the best-fit point. These points can be using as starting points of the minimizer to locate the eight-fold degeneracy. Note that similar methods using the $\chi^2$ instead of the total rates have also been successfully used in the past. 

@@

Finally, note that any degenerate solution below the confidence level threshold which cannot be located makes the result appear better than it actually is. Thus, one should be careful with the determination of the degenerate solutions in order to find all of them.

@@

In this chapter, we discuss possibilities to obtain low-level information
in \GLOBES , \ie, about oscillation probabilities, rates, and other
information lower than on the $\chi^2$-level.

@@

\GLOBES\ can compute the probabilities in vacuum
with the following function:
\begin{function}
\GLBNS{VacuumProbability}
{\tt double glbVacuumProbability(int l, int m, int panti,double E, double L)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} and the baseline {\tt L} in vacuum. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos. 
\end{function}
Note that for this and the other probability functions $1 \le$ {\tt l}, {\tt m} $\le 3$.
In addition, the oscillation probabilities in matter can be obtained
with:
\begin{function}
\GLBNS{ProfileProbability}
{\tt double glbProfileProbability(int exp, int l, int m, int panti,double E)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} in matter, where the matter density profile
is the one of experiment {\tt exp}. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos.
The matter density profile including baseline is the one from the last
evaluated experiment. 
\end{function}
For a constant matter density profile, it is sufficient to specify the oscillation channel with
\begin{function}
\GLBNS{ConstantDensityProbability}
{\tt double glbConstantDensityProbability(int l, int m, int panti, double E, double L, double rho)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} in constant matter, where the matter density profile
has the constant density {\tt rho} and the baseline is {\tt L}. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos.
\end{function}
If one in addition wants to use the low-pass filter feature in \GLOBES\ (see \Sec~\ref{sec:energy}), can can use
\begin{function}
\GLBNS{FilteredConstantDensityProbability}
{\tt double glbFilteredConstantDensityProbability(int exp, int l, int m, int panti, double E)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} in constant matter, where the matter density and baseline, as well as the filter properties are taken from experiment {\tt exp}. The parameter {\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos.
\end{function}

@@

In some cases, it is necessary to obtain information from the \AEDL\
files. Very basic information is supplied with
\begin{function}
\GLBNS{GetEminEmax}
{\tt int glbGetEminEmax(int experiment, double *emin, double *emax)} returns the
energy range [{\tt emin},{\tt emax}] covered by the binning as defined in the AEDL file for the experiment
{\tt experiment}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindow}
{\tt int glbGetEnergyWindow(int exp, int rule, double *low, double *high)} returns the
energy window [{\tt low},{\tt high}] defined in the AEDL file for the experiment
{\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindowBins}
{\tt int glbGetEnergyWindowBins(int exp, int rule, int *lowbin, int *highbin)} returns the
energy window in terms of bin numbers [{\tt lowbin},{\tt highbin}] corresponding to the energy window defined in the AEDL file for the experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfBins}
{\tt int glbGetNumberOfBins(int exp)} returns the number of bins for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfSamplingPoints}
{\tt int glbGetNumberOfSamplingPoints(int exp)} returns the number of sampling points for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinSizeListPtr}
{\tt double *glbGetBinSizeListPtr(int exp)} returns a pointer to the array of bin widths
for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingStepsizeListPtr}
{\tt double *glbGetSamplingStepsizeListPtr(int exp)} returns a pointer to the array of
sampling step sizes for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinCentersListPtr}
{\tt double *glbGetBinCentersListPtr(int exp)} returns a pointer to the array of
mean bin energies for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingPointsListPtr}
{\tt double *glbGetSamplingPointsListPtr(int exp)} returns a pointer to the array of
sampling points for the experiment {\tt exp}.
\end{function}

@@

\index{norm}{AEDL@\AEDL!names}
Since in \AEDL\ rules, cross section, fluxes etc. carry a `name' by
which they can be refered to and in C they cary only an integer as
index it is sometimes difficult to figure out the correct correspondence.
Therefore the information about this correspondence obtained during
parsing is stored and can be accessed within C by these two functions.
\begin{function}
\GLBNS{NameToValue}
{\tt int glbNameToValue(int exp, const char* context, const char *name)}
Converts an \AEDL\ name given as argument {\tt name} into the corresponding
C index. The variable {\tt context} describes wether this name belongs
to a rule, channel, flux, energy or cross type environment. {\tt exp}
is the number of the experiment and can not be {\tt GLB\_ALL}. It returns
either the index in case of success or {\tt -1} in case the name was not
found. 
\end{function}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Event rates}
\index{norm}{Event rates}
\label{sec:event_rates}
One can also return event rates in \GLOBES , but this feature
requires some knowledge about the experiment definition. 
In fact, many of these functions are very advanced, which means
that the reader who wants to use them should be familiar with
\Secs~\ref{sec:channel} and~\Sec~\ref{sec:rules} of the \AEDL\ manual.
Note that some of the event rate access has changed in \GLOBES\ 3.0,
because user-defined systematics requires very fast access which was
not possible with the old method.

@@

There are several functions to directly print or save the event rate
information:
\begin{function}
\GLBNS{ShowRuleRates}
{\tt int glbShowRuleRates(FILE* stream, int exp, int rule, int pos,
int effi, int bgi, int coeffi, int signal)} prints the binned rule rates as
list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific rule {\tt rule} have to be chosen, as well as the signal
or background rate {\tt signal} (either \GLBC{GLB\_SIG} or \GLBC{GLB\_BG}).
The position {\tt pos} refers to the component within the signal or 
background, and can also be {\tt GLB\_ALL}. The function may return
the rates with (\GLBC{GLB\_W\_COEFF}) or without (\GLBC{GLB\_WO\_COEFF})
overall efficiency coefficient, as it is specified by {\tt coeffi}. 
In addition, it may contain the post-smearing efficiencies (set
{\tt effi} to \GLBC{GLB\_W\_EFF} or \GLBC{GLB\_WO\_EFF}), and the
post-smearing backgrounds (set
{\tt bgi} to \GLBC{GLB\_W\_BG} or \GLBC{GLB\_WO\_BG}). The pre-smearing
efficiencies and backgrounds cannot be accessed at the rule level.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}
\begin{function}
\GLBNS{ShowChannelRates}
{\tt int glbShowChannelRates(FILE *stream,
int exp, int channel, int smearing, int effi, int bgi)}
prints the binned channel rates as
list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific channel {\tt channel} have to be chosen.
The function may return
the rates before (\GLBC{GLB\_PRE}) or after (\GLBC{GLB\_POST})
the energy smearing, as it is specified by {\tt smearing}.
In addition, it may contain the pre- and post-smearing efficiencies (set
{\tt effi} to \GLBC{GLB\_W\_EFF} or \GLBC{GLB\_WO\_EFF}), and the
pre- and post-smearing backgrounds (set
{\tt bgi} to \GLBC{GLB\_W\_BG} or \GLBC{GLB\_WO\_BG}). Note that
the post-smearing efficiencies and backgrounds cannot be taken into
account if the rates are returned before the energy smearing.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}

\index{norm}{Event rates}
For rate vectors, \GLOBES\ currently supports rule-based and channel-based event rate functions, where typically pointers on the rate vectors are returned. The following pointer-based functions are currently supported:
\begin{function}
\GLBNS{GetChannelRatePtr}
{\tt double *glbGetChannelRatePtr(int exp, int ch, int pre\_post)} returns a 
pointer on the simulated rate vector of experiment {\tt exp} and channel {\tt ch}. Either
pre-smearing ({\tt pre\_post} is {\tt GLB\_PRE}) or post-smearing ({\tt pre\_post} is {\tt GLB\_POST})
rates can be accessed.
\end{function}
\begin{function}
\GLBNS{GetRuleRatePtr}
{\tt double *glbGetRuleRatePtr(int exp, int rule)} returns a 
pointer on the simulated rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetSignalRatePtr}
{\tt double *glbGetSignalRatePtr(int exp, int rule)} returns a 
pointer on the simulated signal rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetBGRatePtr}
{\tt double *glbGetBGRatePtr(int exp, int rule)} returns a 
pointer on the simulated background rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetChannelFitRatePtr}
{\tt double *glbGetChannelFitRatePtr(int exp, int ch, int pre\_post)} returns a 
pointer on the fit rate vector of experiment {\tt exp} and channel {\tt ch}. Either
pre-smearing ({\tt pre\_post} is {\tt GLB\_PRE}) or post-smearing ({\tt pre\_post} is {\tt GLB\_POST})
rates can be accessed.
\end{function}
\begin{function}
\GLBNS{GetSignalFitRatePtr}
{\tt double *glbGetSignalFitRatePtr(int exp, int rule)} returns a 
pointer on the fit signal rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetBGFitRatePtr}
{\tt double *glbGetBGFitRatePtr(int exp, int rule)} returns a 
pointer on the fit background rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
A simple example how to use these functions to print a rate vector is
\begin{quote}
{\tt
 int i; \\
   int n\_bins = glbGetNumberOfBins(EXP\_FAR); \\
  double *true\_rates\_N = glbGetRuleRatePtr(0, 0); \\
  printf("Simulated rates, experiment 0, rule 0: $\backslash$n"); \\
  for(i=0;i<n\_bins;i++) printf("\% g ",true\_rates\_N[i]); \\
  printf("$\backslash$n");
}
\end{quote}

>>>>

In many cases, one can find the exact position of the 
$\mathrm{sgn}(\ldm)$-degeneracy with \GLB{ChiAll}, where one starts 
the local minimizer at the suspected position 
and lets it run into the minimum.  The following code excerpt  corresponds to finding the degenerate solution for the example on
  page~\pageref{ex:corrth13dcp}, and it is from {\tt example3.c}: 
\begin{quote}
{\tt
{\footnotesize
  /* Set starting vales to suspected position at opposite sign of ldm */ \\
  \mbox{glbDefineParams(starting\_values,theta12,theta13,theta23,deltacp,sdm,-ldm);} \\
  glbSetDensityParams(starting\_values,1.0,GLB\_ALL); \\
  \\
  /* Set input errors for external input, where some information on ldm \\
   \hspace*{0.5cm} is imposed in order to avoid falling into the right-sign solution */ \\
  glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,ldm/3); \\ 
  glbSetDensityParams(input\_errors,0.05,GLB\_ALL); \\
  \\
  glbSetCentralValues(starting\_values); \\
  glbSetInputErrors(input\_errors); \\
  \\
  /* Localize degenerate solution by minimization over all parameters */ \\
  double CL=glbChiAll(starting\_values,deg\_pos,GLB\_ALL); \\
   \\
  \mbox{/* Now: CL is the chi2 of the deg.~solution and deg\_pos the position */} 
}}
\end{quote}

Using {\tt deg\_pos} to obtain a section of the degeneracy in the
$\stheta$-$\deltacp$-plane (\cf, {\tt example3.c}), one can plot it as a contour plot in addition to the original solution (2 d.o.f., gray curves):
\begin{center}
\colorbox{white}{\includegraphics[width=7.5cm]{correntex}}
\end{center}

@@

\label{mass_ordering}
\index{norm}{Mass hierarchy}
\paragraph{Note:} Inverting the mass hierarchy is not
precisely the same as changing from $\Delta m^2_{31}
\rightarrow -\Delta m^2_{31}$.
In this case the absolute value of $\Delta m^2_{32}$ changes also, which
introduces a new frequency to the problem. Therefore, if we assume
normal hierarchy  whenever $\Delta m^2_{31}>0$, the corresponding
point in parameters space for inverted hierarchy is given by $\Delta 
m^2_{31}\rightarrow - \Delta m^2_{31} + \Delta m^2_{21}$, because
with this defintion the absolute value of  $\Delta m^2_{32}$ is unchanged
and no new frequency is introduced.\\

@@

In addition to switching off the systematics, it can be useful to reduce the input errors during some steps of the localization process in order to prevent the minimizer from running away too far from the targeted solution.

@@

\item[Manual scan of a subspace.] In some cases, the minimizer easily ends up in the wrong/unwanted solution, which is in most cases the already known best-fit solution. For example, when locating the octant degeneracy, it is difficult to prevent the minimizer from running into the best-fit octant. In this case, one can scan one parameter (such as $\theta_{23}$) on a grid by choosing only valid values, and use {\tt glbChiNP} to marginalize over the other ones (while keeping \eg\ $\theta_{23}$ fixed). Therefore, the 6-parameter minimization is split into a 1-parameter manual minimization and a 5-parameter simultaneous minimization. Advantage: Runs with all \GLOBES\ versions. Disadvantage: Very slow. 

@@

 Altogether, there is a maximum of eight intersection points in the $\sin^2 2 \theta_{13}$-$\delta_{\mathrm{CP}}$-plane, one of which is the best-fit point. These points can be used as starting points for the minimizer to locate the eight-fold degeneracy. Note that similar methods using the $\chi^2$ instead of the total rates have also been successfully used in the past. 

@@

Finally, note that any degenerate solution below the confidence level threshold, which cannot be located, makes the result appear better than it actually is. Thus, one should be careful with the determination of the degenerate solutions in order to find all of them.

@@

In this chapter, we discuss possibilities to obtain low-level information
in \GLOBES , \ie, oscillation probabilities, rates, and other
information lower than on the $\chi^2$-level.

@@

\GLOBES\ can compute the probabilities in vacuum
with the following function:
\begin{function}
\GLBNS{VacuumProbability}
{\tt double glbVacuumProbability(int l, int m, int panti,double E, double L)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} and the baseline {\tt L} in vacuum. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos. 
\end{function}
Note that for this and the other probability functions $1 \le$ {\tt l}, {\tt m} $\le 3$.
In addition, the oscillation probabilities in matter can be obtained
with:
\begin{function}
\GLBNS{ProfileProbability}
{\tt double glbProfileProbability(int exp, int l, int m, int panti,double E)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} in matter, where the matter density profile
is the one of experiment {\tt exp}. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos.
\end{function}
For a constant matter density profile, it is sufficient to specify the oscillation channel with
\begin{function}
\GLBNS{ConstantDensityProbability}
{\tt double glbConstantDensityProbability(int l, int m, int panti, double E, double L, double rho)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} in constant matter, where the matter density profile
has the constant density {\tt rho} and the baseline is {\tt L}. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos.
\end{function}
If one in addition wants to use the low-pass filter feature in \GLOBES\ (see \Sec~\ref{sec:energy}), one can can use
\begin{function}
\GLBNS{FilteredConstantDensityProbability}
{\tt double glbFilteredConstantDensityProbability(int exp, int l, int m, int panti, double E)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} in constant matter, where the matter density and baseline, as well as the filter properties are taken from experiment {\tt exp}. The parameter {\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos.
\end{function}

@@

In some cases, it is necessary to obtain information from the \AEDL\
files. Very basic information is supplied with
\begin{function}
\GLBNS{GetEminEmax}
{\tt int glbGetEminEmax(int experiment, double *emin, double *emax)} returns the
energy range [{\tt emin}, {\tt emax}] covered by the binning as defined in the AEDL file for the experiment
{\tt experiment}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindow}
{\tt int glbGetEnergyWindow(int exp, int rule, double *low, double *high)} returns the
energy window [{\tt low}, {\tt high}] defined in the AEDL file for the experiment
{\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindowBins}
{\tt int glbGetEnergyWindowBins(int exp, int rule, int *lowbin, int *highbin)} returns the
energy window in terms of bin numbers [{\tt lowbin}, {\tt highbin}] corresponding to the energy window defined in the AEDL file for the experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfBins}
{\tt int glbGetNumberOfBins(int exp)} returns the number of bins for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfSamplingPoints}
{\tt int glbGetNumberOfSamplingPoints(int exp)} returns the number of sampling points for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinSizeListPtr}
{\tt double *glbGetBinSizeListPtr(int exp)} returns a pointer to the array of bin widths
for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingStepsizeListPtr}
{\tt double *glbGetSamplingStepsizeListPtr(int exp)} returns a pointer to the array of
sampling step sizes for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinCentersListPtr}
{\tt double *glbGetBinCentersListPtr(int exp)} returns a pointer to the array of
mean bin energies for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingPointsListPtr}
{\tt double *glbGetSamplingPointsListPtr(int exp)} returns a pointer to the array of
sampling points for the experiment {\tt exp}.
\end{function}

@@

\index{norm}{AEDL@\AEDL!names}
Since in \AEDL\, rules, cross section, fluxes etc. carry a `name' by
which they can be refered to, while in C they carry only an integer
index, it is sometimes difficult to figure out the correct correspondence.
Therefore the information about this correspondence obtained during
parsing is stored and can be accessed within C by the following two functions.
\begin{function}
\GLBNS{NameToValue}
{\tt int glbNameToValue(int exp, const char* context, const char *name)}
Converts an \AEDL\ name given as argument {\tt name} into the corresponding
C index. The variable {\tt context} describes wether this name belongs
to a rule, channel, flux, energy, or cross type environment. {\tt exp}
is the number of the experiment and can not be {\tt GLB\_ALL}. It returns
either the index in case of success or {\tt -1} in case the name was not
found. 
\end{function}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Event rates}
\index{norm}{Event rates}
\label{sec:event_rates}
One can also return event rates in \GLOBES , but this feature
requires some knowledge about the experiment definition. 
In fact, many of these functions are very advanced, which means
that the reader who wants to use them should be familiar with
\Secs~\ref{sec:channel} and~\Sec~\ref{sec:rules} of the \AEDL\ manual.
Note that parts of the event rate access have changed in \GLOBES\ 3.0,
because user-defined systematics require very fast access, which was
not possible with the old method.

@@

There are several functions to directly print or save the event rate
information:
\begin{function}
\GLBNS{ShowRuleRates}
{\tt int glbShowRuleRates(FILE* stream, int exp, int rule, int pos,
int effi, int bgi, int coeffi, int signal)} prints the binned rule rates as
a list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific rule {\tt rule} have to be chosen, as well as the signal
or background rate {\tt signal} (either \GLBC{GLB\_SIG} or \GLBC{GLB\_BG}).
The position {\tt pos} refers to the component within the signal or 
background, and can also be {\tt GLB\_ALL}. The function may return
the rates with (\GLBC{GLB\_W\_COEFF}) or without (\GLBC{GLB\_WO\_COEFF})
overall efficiency coefficient, as it is specified by {\tt coeffi}. 
In addition, it may contain the post-smearing efficiencies (set
{\tt effi} to \GLBC{GLB\_W\_EFF} or \GLBC{GLB\_WO\_EFF}), and the
post-smearing backgrounds (set
{\tt bgi} to \GLBC{GLB\_W\_BG} or \GLBC{GLB\_WO\_BG}). The pre-smearing
efficiencies and backgrounds cannot be accessed at the rule level.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}
\begin{function}
\GLBNS{ShowChannelRates}
{\tt int glbShowChannelRates(FILE *stream,
int exp, int channel, int smearing, int effi, int bgi)}
prints the binned channel rates as
a list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific channel {\tt channel} have to be chosen.
The function may return
the rates before (\GLBC{GLB\_PRE}) or after (\GLBC{GLB\_POST})
the energy smearing, as it is specified by {\tt smearing}.
In addition, it may contain the pre- and post-smearing efficiencies (set
{\tt effi} to \GLBC{GLB\_W\_EFF} or \GLBC{GLB\_WO\_EFF}), and the
pre- and post-smearing backgrounds (set
{\tt bgi} to \GLBC{GLB\_W\_BG} or \GLBC{GLB\_WO\_BG}). Note that
the post-smearing efficiencies and backgrounds cannot be taken into
account if the rates are returned before the energy smearing.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}

\index{norm}{Event rates}
For rate vectors, \GLOBES\ currently supports rule-based and channel-based event rate functions, where typically pointers on the rate vectors are returned. The following pointer-based functions are currently supported:
\begin{function}
\GLBNS{GetChannelRatePtr}
{\tt double *glbGetChannelRatePtr(int exp, int ch, int pre\_post)} returns a 
pointer to the simulated rate vector of experiment {\tt exp} and channel {\tt ch}. Either
pre-smearing ({\tt pre\_post} is {\tt GLB\_PRE}) or post-smearing ({\tt pre\_post} is {\tt GLB\_POST})
rates can be accessed.
\end{function}
\begin{function}
\GLBNS{GetRuleRatePtr}
{\tt double *glbGetRuleRatePtr(int exp, int rule)} returns a 
pointer to the simulated rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetSignalRatePtr}
{\tt double *glbGetSignalRatePtr(int exp, int rule)} returns a 
pointer to the simulated signal rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetBGRatePtr}
{\tt double *glbGetBGRatePtr(int exp, int rule)} returns a 
pointer to the simulated background rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetChannelFitRatePtr}
{\tt double *glbGetChannelFitRatePtr(int exp, int ch, int pre\_post)} returns a 
pointer to the fit rate vector of experiment {\tt exp} and channel {\tt ch}. Either
pre-smearing ({\tt pre\_post} is {\tt GLB\_PRE}) or post-smearing ({\tt pre\_post} is {\tt GLB\_POST})
rates can be accessed.
\end{function}
\begin{function}
\GLBNS{GetSignalFitRatePtr}
{\tt double *glbGetSignalFitRatePtr(int exp, int rule)} returns a 
pointer to the fit signal rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetBGFitRatePtr}
{\tt double *glbGetBGFitRatePtr(int exp, int rule)} returns a 
pointer to the fit background rate vector of experiment {\tt exp} and rule {\tt rule}.
\end{function}
A simple example how to use these functions to print a rate vector is
\begin{quote}
{\tt
 int i; \\
   int n\_bins = glbGetNumberOfBins(EXP\_FAR); \\
  double *true\_rates\_N = glbGetRuleRatePtr(0, 0); \\
  printf("Simulated rates, experiment 0, rule 0: $\backslash$n"); \\
  for(i=0;i<n\_bins;i++) printf("\% g ",true\_rates\_N[i]); \\
  printf("$\backslash$n");
}
\end{quote}
